---
title: "Model Validation for Scenario 03 - Release 05"
output:
  html_document:
    df_print: paged
---
### REFERENCES ----------------------------------------------------------------------------------
CHOI, Chulho; KANG, Yeonsik. Simultaneous braking and steering control method based on nonlinear model predictive control for emergency driving support. International Journal of Control, Automation and Systems, v. 15, n. 1, p. 245-252, 2017.

MAHMUD, SM Sohel et al. Application of proximal surrogate indicators for safety evaluation: A review of recent developments and research needs. IATSS research, v. 41, n. 4, p. 152-162, 2017.

SCURLOCK, Bob J.; IPSER, James R. Illustrations of equivalent methods to reproduce vehicle and occupant dynamics as a pedagogical tool. arXiv preprint arXiv:1404.1542, 2014.

XIE, Kun et al. Use of real-world connected vehicle data in identifying high-risk locations based on a new surrogate safety measure. Accident Analysis & Prevention, v. 125, p. 211-219, 2019.

YANG, Hong. Simulation-based evaluation of traffic safety performance using surrogate safety measures. 2012. Thesis. Rutgers University-Graduate School-New Brunswick.

```{r}
library(tidyverse)
library(caret)
library(nlme)
library(ISLR)
library(glm2)
library(ISLR)
library(glm2)
library(ggplot2)
library(plotly)
require(plotly)
require(tidyverse)
require(caret)
require(nlme)
require(ISLR)
require(glm2)
require(ISLR)
require(glm2)
require(ggplot2)
```
### FUNCTIONS DECLARATION
```{r}
# 0.1)Safe Stopping Distance FUNCTION
# A função SSD(Safe Stopping Distance) serve para calcular a distância segura de parada para a velocidade selecionada do veículo em questão (Automóvel ou Caminhão). O resultado que ela retorno está no Sistema Intenacional; ou seja, metros.
SSD <- function(velocity, vehicle)
{
  alphaA <-  85.372284
  betaA  <-   0.007908
  thetaA <- -90.859372
  alphaT <-  92.91
  betaT  <- 0.008481
  thetaT <- -100.9
  if (vehicle=="A")
  { DTa_calc <- alphaA*exp(betaA*velocity)+thetaA
    return (DTa_calc)}
  else
  { DTt_calc <- alphaT*exp(betaT*velocity)+thetaT
    return (DTt_calc)}
}
#SSD(150, "A") 
#Teste da função: 
#SSD(150, "A") = 188.7019
################################ DELTA S #######################################
#0.2) DISPLACEMENT
#s = s0 + v0t + at^2/2
DeltaS <- function(v0, a, t){
  return(v0*t + a*(t^2)/2)
}
############ Ds (Critical Distance during deceleration) ########################
Ds <- function(vf1, vl1, af1, al1, Tbc1=0.15, Thum1=1.2, Tbr1 =0.45,  D0_1=2)
{ if(al1==0)
    al1 <- 0.1
  if(af1==0)
    af1 <- 0.1
  vrel <- vf1 - vl1
  h1 <- vl1^2/(2*al1)
  f1 <- vf1^2/(2*af1)
  respDs <- h1 - f1 + vl1*(Tbc1 + Thum1) + vrel*Tbr1/2 + D0_1
 
  return(respDs)
}
################################   DSS   ######################################
# 1) Difference of Space distance and Stopping distance- DSS: REF 45 from Mahmud(2017).
DSS <- function(Vf, Vl, dT, u, dist, g) {
  # VF = Following Vehicle Speed
  # VL = Leader Vehicle Speed
  # dT = Reaction time (Mean Reaction time = 1.5s)
  # u = Friction Coefficient (DRY = 0.7 and WET = =.4)
  # dist = distance between Leading vehicle and Following vehicle [m]
  # g = Gravity Acceleraiton (9.8)
  DSSf <- (Vf^2)/(2*u*g)
  DSSl <- dT*Vl^2 + (Vl^2)/(2*u*g)
  return(DSSf - DSSl)
}
###############################################################################
# 2)Distance between vehicles
# A função dist permite Calcular a Distância (em metros) a partir das coords. geográficas Latitude e longitude p/ 2ptos
dist <- function(lat1, lon1, lat2, lon2)
{
  #Conversão de latitude
  clat1 <- lat1*110.574657
  clat2 <- lat2*110.574657

  #Conversão de longitude
  clon1 <- lon1*111.319892
  clon2 <- lon2*111.319892

  #Cálculo de distância
  plat <- clat2 - clat1
  plon <- clon2 - clon1
  
  plat2 <- plat ^ 2
  plon2 <- plon ^ 2
  out <- sqrt(plon2 + plat2) 
  return (out*1000) #Retorna saída em metros
}
################################### TTC #######################################
# 3)Time To Collision - TTC: (MAHMUD, 2017).

# A função TTC irá calcular o tempo para colisão
TTC <- function(dist, Lv, Vf, Vl) # dist = Distance between vehicles,       Lv = length of leading vehicle
{                                 #   Vf = Following vehicle,                Vl = Leading vehicle
    divisor <- Vf - Vl
    if(divisor==0)
    {divisor <-0.1}
    calcTTC <- (dist - Lv)/(divisor)
    return (calcTTC)
}
#Teste da função:
#TTC(25, 5, 20, 10) =2
################################### CIF ######################################
# 4) Criticality Index Function - CIF (CIF = V^2/TTC)
# ----------------------------------------------------
#    C.Y. Chan, Defining safety performance measures of driver-assistance systems for intersection left-turn 
#    conflicts, Intelligent Vehicles Symposium, 2006 IEEEIEEE, 2006.
CIF <- function(V, TTCi){
  return(V^2/TTCi)
}
################################### TTCD ######################################
# 5) Time to collision with disturbance - TTCD: (XIE, 2019)

# Time to collision with disturbance - TTCD
TTCD <- function(i, V1, V2, L0, Lv, d){

#Vl = v1 = Speed of the leading vehicle
#Vf = v2 = Speed of the following vehicle (constant in the car following scenario)  
#L0 = Initial relative distance between the leading and the following vehicle
#Lv = length of leading vehicle
# d = The deceleration rate of the leading vehicle
    if(d <= 0)
    {d <- 0.1}

  verifica <- (2*V1*V2 - V1*V1)/(2*(L0-Lv))

  if(d<=verifica){
    difV <- V1-V2
    difL <- L0 - Lv
    raiz <- difV*difV + 2*abs(d)*difL
    TTCDcalc = (difV + sqrt(raiz))/d
    }
  else {
    difL <- L0 - Lv
    if(V2==0){V2<-0.1}
    numerador <- 2*d*difL + V1^2
    TTCDcalc = numerador/(2*d*V2)
    }
  return(TTCDcalc)
}
#Teste da função:
#View(TTCD(1, 1, 10, 5, 10))
################################################################################
# 5.1) iTTCD
iTTCD <- function(TTCDvalue)
{ #OBS: Como o TTCD quanto maior o valor menor o risco de colisão, deve-se inverter o algortmo para iTTCD
  if(TTCDvalue >=100)
    {resp <- 100}
  else if(TTCDvalue>1 && TTCDvalue<100)
    {resp <- TTCDvalue}
  else if(TTCDvalue==0)
    {resp <- 0.1}
  else if(TTCDvalue<0 && TTCDvalue>-1)
    {resp <- 1/TTCDvalue*(-1)}
  else 
    {resp <- TTCDvalue*(-1) }
  return(resp)
}
################################### DRAC ######################################
# 6) Deceleration Rate to Avoid Crash - DRAC: (MAHMUD, 2017).

# Deceleration Rate to Avoid Crash (DRAC)
DRAC <- function(Vf, Vl, dist, Lv)    # v1 = Initial speed of the leading vehicle [m/s]
{                                     # v2 = Initial speed of the following vehicle (constant in the car following scenario)
                                      # dist = Distance between vehicles [m]
                                      # Lv = length of leading vehicle [m]
  calcDRAC <- ((Vf-Vl)^2)/(2*(dist-Lv))
  return (calcDRAC)
}
#Teste da função:
# DRAC(2, 1, 10, 5)=0.1
####################################
# 7)iDRAC
iDRAC <- function(DRACvalue)
{
  if(DRACvalue<1.5)
    {return(1)}
  else if(DRACvalue<3)
    {return(3)}
  else if(DRACvalue<4.5)
    {return(5)}
  else if(DRACvalue<6)
    {return(7)}
  else
    {return(9)}
}

################################### MTTC #########################################################
# 8) Modified Time to Collision - MTTC: Page 41 (YANG, 2012) ou (MAHMUD, 2017).
MTTC <- function(deltaV, deltaA, D){
  # deltaV = vR = Relative Speed
  # deltaA = Relative Acceleration
       # D = Initial Relative Space Gap
  if(deltaA != 0)
  {
    raiz <- deltaV^2 + 2*deltaA*D
    t1 <- deltaV*(-1) -sqrt(abs(raiz))
    t2 <- deltaV*(-1) +sqrt(abs(raiz))
    if(t1>0 && t2>0)
    {
      if(t1>=t2){
        ProbMTTC.df1 <- data.frame(deltaV, deltaA, D, t1, t2)
        #View(ProbMTTC.df1)
        return(t2)}
      else if(t1<t2){
        ProbMTTC.df2 <- data.frame(deltaV, deltaA, D, t1, t2)
        #View(ProbMTTC.df2)
        return(t1)
        }
    }
    else if(t1>0 && t2<=0)
    { ProbMTTC.df3 <- data.frame(deltaV, deltaA, D, t1, t2)
      #View(ProbMTTC.df3)
      return(t1)  }
    else if(t1<0 && t2>0)
    {
      ProbMTTC.dF4 <- data.frame(deltaV, deltaA, D, t1, t2)
      #View(ProbMTTC.dF4)
      return(t2)}
  }
  else if(deltaA==0 && deltaV>0)
  {
    if(D==0){D<-0.1}
    ProbMTTC.df5 <- data.frame(deltaV, deltaA, D, t1, t2)
    #View(ProbMTTC.df5)
    return(D/deltaV)}
  else
  {
    if(D==0){D<-0.1}
    if(deltaV==0){deltaV<-0.1}
    return(D/deltaV)}
}
#View(MTTC(-70, 0, 0))
###############################################################################
# 8.1) iMTTC
iMTTC <- function(MTTCvalue)
{
  if(MTTCvalue >=100)
    {resp <- 100}
  else if(MTTCvalue>0 && MTTCvalue<100)
    {resp <- MTTCvalue}
  else if(MTTCvalue==0)
    {resp <- 0.1}
  else if(MTTCvalue<0 && MTTCvalue>-1)
    {resp <- MTTCvalue*(-1)}
  else 
    {resp <- 1/(MTTCvalue*(-1)) }
  return(resp)
}
####################################### CI ####################################################
# 9) Crash Index: veja referência (MAHMUD, 2017)
CI <- function(vf, af, MTTCi, vl, al){
  # vf    = Folowing Vehicle Speed
  # vl    = Leading Vehicle Speed
  # af    = Following Vehicle Acceleraiton
  # al    = Leading Vehicle Acceleraiton  
  # MTTCi = Modified Time to Collision index
  factor1 <- (vf + af*MTTCi)^2
  factor2 <- (vl + al*MTTCi)^2
  return((1/MTTCi)*(factor1-factor2)/2.0)
}
###############################################################################
# 9.1) iCI
iCI <- function(CIvalue)
{
  if(CIvalue >=100)
    {resp <- 100}
  else if(CIvalue>0 && CIvalue<100)
    {resp <- CIvalue}
  else if(CIvalue==0)
    {resp <- 0.1}
  else if(CIvalue<0 && CIvalue>-1)
    {resp <- CIvalue*(-1)}
  else 
    {resp <- 1/(-CIvalue) }
  return(resp)
}
###############################################################################################################
# 10) CPi: ver pág. 43 da referência (YANG, 2012)
CPi <- function(MTTCvalue)
{
  lambda <- 1.4419*MTTCvalue - 0.0012
  Fator <- (-1)*MTTCvalue/lambda
  return(exp(Fator))
}
############# Vá para a LINHA 315 e clique no Triângulo EXECUTAR ##############
```

# AHP FUNCTION MODEL - Release 5.0 (By Massaki de O. Igarashi)
```{r}
AHP <- function(PS11, PS12, PS13, PS14, PS15,
                PS21, PS22, PS23, PS24, PS25,
                PS31, PS32, PS33, PS34, PS35,
                PS41, PS42, PS43, PS44, PS45,
                PS51, PS52, PS53, PS54, PS55,
                C11,  C16,  C21,  C26,  C31){
  
# c11 = iTTCD  input value
# c16 = iDRAC  input value
# c21 = iMTTC  input value
# c26 = iCI    input value
# c31 = IDdist input value
  
# Matriz AVN
#            iTTCD    iDRAC    iMTTC      iCI     iDdist 
# iTTCD      PS11     PS12      PS13      PS14    PS15
# iDRAC      PS21     PS22      PS23      PS24    PS25
# iMTTC      PS31     PS32      PS33      PS34    PS35
# iCI        PS41     PS42      PS43      PS44    PS45
# IdDIST     PS51     PS52      PS53      PS54    PS55
#------------------------------------------------------
#SOMATORIO   PST1     PST2      PST3      PST4    pst5
  
  PS <- matrix(c(
              c(PS11, PS12, PS13, PS14, PS15),
              c(PS21, PS22, PS23, PS24, PS25),
              c(PS31, PS32, PS33, PS34, PS35),
              c(PS41, PS42, PS43, PS44, PS45),              
              c(PS51, PS52, PS53, PS54, PS55)), byrow=TRUE, nrow=5)
  colnames(PS)<-c("TTCD", "DRAC", "MTTC", "CI", "Ddist") 
  rownames(PS)<-c("TTCD", "DRAC", "MTTC", "CI", "Ddist") 
  #View(PS)
  PST <- colSums(PS, na.rm = FALSE, dims = 1)

  AV1 <- sqrt(PS11*PS12*PS13*PS14*PS15)
  AV2 <- sqrt(PS21*PS22*PS23*PS24*PS25)
  AV3 <- sqrt(PS31*PS32*PS33*PS34*PS35)
  AV4 <- sqrt(PS41*PS42*PS43*PS44*PS45)
  AV5 <- sqrt(PS51*PS52*PS53*PS54*PS55)
  AVT <- AV1 + AV2 + AV3 + AV4 + AV5
  AVN1 <- AV1/AVT
  AVN2 <- AV2/AVT
  AVN3 <- AV3/AVT
  AVN4 <- AV4/AVT
  AVN5 <- AV5/AVT

  LambdaMAX <- PST[1]*AVN1 + PST[2]*AVN2 + PST[3]*AVN3 + PST[4]*AVN4 + PST[5]*AVN5
  n <- 5 #Pois tenho 5 critérios
  CI <- (LambdaMAX - n)/(n-1)
  CR <- CI/1.1086 #Ver pág. 25 do livro do Mateo Brunelli sobre AHP
 
  # MATRIZ TTCD*
  B11 <- 1
  B12 <- 1/C11
  B13 <- B11 + B12
  #C11 IS INPUT VALUE
  C12 <- 1
  C13 <- C11 + C12
  D11 <- sqrt(abs(B11*C11))
  D12 <- sqrt(abs(B12*C12))
  D13 <- D11 + D12
  AVN_TTCD_1 <- D11/D13
  AVN_TTCD_2 <- D12/D13
  AVN_TTCD_T <- AVN_TTCD_1 + AVN_TTCD_2
  
  # MATRIZ DRAC*
  B16 <- 1
  B17 <- 1/C16
  B18 <- B16 + B17
  #C16 IS INPUT VALUE 
  C17 <- 1
  C18 <- C16 + C17
  D16 <- sqrt(B16*C16)
  D17 <- sqrt(B17*C17)
  D18 <- D16 + D17
  AVN_DRAC_1 <- D16/D18
  AVN_DRAC_2 <- D17/D18
  AVN_DRAC_T <- AVN_DRAC_1 + AVN_DRAC_2
  
  # MATRIZ MTTC
  B21 <- 1
  B22 <- 1.0/C21
  B23 <- B21 + B22
  #C21 IS INPUT VALUE
  C22 <- 1
  C23 <- C21 + C22
  D21 <- sqrt(B21*C21)
  D22 <- sqrt(B22*C22)
  D23 <- D21 + D22
  AVN_MTTC_1 <- D21/D23
  AVN_MTTC_2 <- D22/D23
  AVN_MTTC_T <- AVN_MTTC_1 + AVN_MTTC_2
  
  # MATRIZ CI
  B26 <- 1
  B27 <- 1/C26
  B28 <- B26 + B27
  #C26 IS INPUT VALUE
  C27 <- 1
  C28 <- C26 + C27
  D26 <- sqrt(B26*C26)
  D27 <- sqrt(B27*C27)
  D28 <- D26 + D27
  AVN_CI_1 <- D26/D28
  AVN_CI_2 <- D27/D28
  AVN_CI_T <- AVN_CI_1 + AVN_CI_2
  
  # MATRIZ Ddist
  B31 <- 1
  B32 <- 1/C31
  B33 <- B31 + B32
  #C31 IS INPUT VALUE
  C32 <- 1
  C33 <- C31 + C32
  D31 <- sqrt(B31*C31)
  D32 <- sqrt(B32*C32)
  D33 <- D31 + D32
  AVN_Ddist_1 <- D31/D33
  AVN_Ddist_2 <- D32/D33
  AVN_Ddist_T <- AVN_Ddist_1 + AVN_Ddist_2
  
  # OPÇÕES DE DECISÃO ###################################################################
  DANGEROUS <- 100*(AVN1*AVN_TTCD_1 + AVN2*AVN_DRAC_1 + AVN3*AVN_MTTC_1 + AVN4*AVN_CI_1 + AVN5*AVN_Ddist_1)
       SAFE <- 100*(AVN1*AVN_TTCD_2 + AVN2*AVN_DRAC_2 + AVN3*AVN_MTTC_2 + AVN4*AVN_CI_2 + AVN5*AVN_Ddist_2)
  if(DANGEROUS>50){decisao <- "DANGEROUS"}
  else {decisao <- "SAFE"}
  outputAHP <- list(decisao, toString(DANGEROUS), toString(SAFE), toString(LambdaMAX), toString(CI), toString(CR*100))
  return(outputAHP)
} 

####################### Go to LINE 450 and CLICK To Execute ###################
```

# INPUTS AND SIMULATIONS  ********************************************************************************
```{r}
# ***********************************************************************************************************
# 0.0) VEHICLES VELOCITIES (VL= LEADING VEHICLE, VF = FOLLOWING VEHICLE)
# ***********************************************************************************************************
t <- seq(12)
VL3 <-c(60, 60, 60,  60, 60, 60, 57.9, 46.7, 21.9, 5.2, 0.9, 0)*0.2778
VF3 <-c(0, 0.9, 2.1, 5.2, 11.4, 21.9, 35.2, 46.7, 53.9, 57.5, 59.1, 60)*0.2778

VelL3.df <- data.frame(x = t, y = 0.2778*VL3) #Multiplica por 0.2778 para converter de km/h para m/s
VelF3.df <- data.frame(x = t, y = 0.2778*VF3)
Vel.df <- data.frame(x = VL3, y = VF3)
DeltaV3 <- VF3 - VL3
# plot VELOCITY data
plot(t, VL3, ylim = c(1,20), type = "b", pch=5, col = "red",  main = "VEHICLES' VELOCITIES", xlab = "Time (s)", ylab = "Velocity [m/s])") 
par(new = TRUE)
lines(t, VF3, ylim = c(1,20), pch=18, type = "b", col = "blue",lty=2) 

# Add a legend to the plot
# Add a legend
legend(9.5, 12, legend=c("Leading", "Following"),
      col=c("red", "blue"), lty=1:2, cex=1)
########### Vá para a LINHA 475 e clique no Triângulo EXECUTAR #################
```


```{r}
#library(plotly)
#require(plotly)
t <- seq(12)
fig <- ggplot(data=Vel.df, aes(x=t)) + labs(title = "VEHICLES' VELOCITIES") + xlab("TIME [s]") + 
  ylab("VELOCITY [m.s-1]") + xlim(1, 12) + ylim(0, 20) +
  geom_line(aes(y = VL3), color = "darkred",   linetype=2, size = 3) + 
  geom_line(aes(y = VF3), color = "black", linetype=6, size = 2) +  
  
  scale_color_manual(name="VEHICLES VELOCITY")+
  guides(colour = guide_legend(override.aes = list(linetype = 1)))
ggplotly(fig)
#################### Vá para a LINHA 490 e clique no Triângulo EXECUTAR ######
```

```{r}
# *****************************************************************************
# 0.1) Acceleration = DeltaV/DeltaT 
# *****************************************************************************
aL3 <- numeric(12)
aF3 <- numeric(12)
for(i in 1:11){
    aL3[i] <- (VL3[i+1]-VL3[i])/(t[i+1]-t[i])
    aF3[i] <- (VF3[i+1]-VF3[i])/(t[i+1]-t[i])
}
aL3[12] <- aL3[11]
aF3[12] <- aF3[11]
AccelL3.df <- data.frame(x = t, y = aL3)
AccelF3.df <- data.frame(x = t, y = aF3)
DeltaA3 <- aF3 - aL3

# plot ACELERATION  data
par(mfrow=c(2, 1))
plot(t, AccelL3.df$y,  type = "b", pch=5, col = "red",  main = "Leader Vehicle Acceleration", xlab = "Time (s)", ylab = "Acceleration[m/s-2])")

plot(t, AccelF3.df$y,  type = "b", pch=18, col = "blue",  main = "Following Vehicle Acceleration", xlab = "Time (s)", ylab = "Acceleration[m/s-2])")

############## Vá para a LINHA 515 e clique no Triângulo EXECUTAR #############
```

```{r}
# *****************************************************************************
# 0.2) Displacement Vectors
# *****************************************************************************
## DeltaS <- function(v0, a, t){

DeltaSvectorF3 <- numeric(12)
DeltaSvectorL3 <- numeric(12)
t <- seq(12)
DeltaS3.df <- data.frame(x = VelF3.df$x, y = DeltaSvectorF3, z = DeltaSvectorL3)
for(i in 1:11){
  DeltaSvectorF3[i] <- DeltaS(VF3[1], aF3[i], VF3[i])
  DeltaSvectorL3[i] <- DeltaS(VL3[1], aL3[i], VL3[i])
}
par(mfrow=c(2, 1))
plot(t, DeltaSvectorL3,  type = "b", pch=5, col = "red",  main = "DeltaS Leading", xlab = "Time (s)", ylab = "DeltaS [m]") 

plot(t, DeltaSvectorF3,  type = "b", pch=5, col = "blue",  main = "DeltaS Following", xlab = "Time (s)", ylab = "DeltaS [m]")

###############################################################################
# 0.3) Ds (Critical Distance during deceleration) ########################
# Ds <- function(vf3, vl3, af3, al3, Tbc1=0.15, Thum1=1.2, Tbr1 =0.45,  D0_1=2)
CDDD <- numeric(12)
for(i in 1:12) {
  CDDD[i] <- Ds(VF3[i], VL3[i], aF3[i], aL3[i], 0.15, 1.2, 0.45,  2)
}
plot(t, CDDD, ylim = c(-1000, 1500), type = "b", pch=5, col = "red", main = "Critical Distance during deceleration", xlab = "Time (s)", ylab = "Critical Distance during deceleration")

# *****************************************************************************
# 0.4)  Cummulative Displacement calculus for this scenario
# PARA ENCONTRAR A REAL POSIÇÃO DE CADA VEÍCULO
# *****************************************************************************
DeltaSLcumullate3 <- cumsum(DeltaSvectorL3)
DeltaSFcumullate3 <- cumsum(DeltaSvectorF3)
DeltaScumullate3.df <- data.frame(x = DeltaSLcumullate3, y = DeltaSFcumullate3)
DeltaSLcumullate3.df <- data.frame(x = t, y = DeltaSLcumullate3)
DeltaSFcumullate3.df <- data.frame(x = t, y = DeltaSFcumullate3)
DeltaScummullate3.df <- data.frame(x = t, y = DeltaSFcumullate3, z = DeltaSLcumullate3)
#Cumulative spatial displacement data PLOT
#par(mfrow=c(2, 1))
plot(t, DeltaSLcumullate3.df$y,  ylim = c(0, 2000), type = "b", pch=5, col = "red",  main = "Cumulative spatial displacement", xlab = "Time (s)", ylab = "Cumulative spatial displacement [m]")
#par(new = TRUE)
lines(t, DeltaSFcumullate3.df$y, ylim = c(0, 2000), pch=18, type = "b", col = "blue",lty=2) 
#legend(8, 50, legend=c("Leader", "Following"), col=c("red", "blue"), lty=1:2, cex=1)

############## Vá para a LINHA 565 e clique no Triângulo EXECUTAR #############
```



```{r}
# *****************************************************************************
# 0.5) Ddist = Distance between vehicles calculus for this Scenario
# *****************************************************************************
Ddist3 <- numeric(12)
iDdist3 <- numeric(12)
for(i in 1:12) {
  Ddist3[i] <- DeltaSLcumullate3.df$y[i] - DeltaSFcumullate3.df$y[i]
  if(Ddist3[i]<=100)
    iDdist3[i] <- (-1)*Ddist3[i] + 100
  else
    iDdist3[i] <- 1.0/Ddist3[i] 
  if(iDdist3[i]>= 100)
    iDdist3[i] <- 100
}
plot(t, Ddist3, ylim = c(-1000, 1500), type = "b", pch=5, col = "black",  main = "Distance between vehicles[m]  x T[s]", xlab = "Time (s)", ylab = "Distance between vehicles[m]")
par(new = TRUE)
lines(t, iDdist3, pch=18, type = "b", col = "red",lty=2)
legend(10, 1450, legend=c("Ddist", "iDdist"), col=c("black", "red"), lty=1:2, cex=1)

Ddist3.df <- data.frame(t, VL3,VF3, Ddist3)
write.csv2(Ddist3.df, "C:\\WYOMING2\\DataFrames\\DistanceBetweenVehiclesCENARIO3_R04.csv")

# ***********************************************************************************************************
# 0.6) Decelaration Rate calculus for this Scenario
# ***********************************************************************************************************
decL3 <- numeric(12) #To create a vector with 12 numbers zero
decF3 <- numeric(12) 
for(i in 1:11) {
  decL3[i] <- aL3[i+1]- aL3[i]
  decF3[i] <- aF3[i+1]- aF3[i]
}
decL3[12] <- decL3[11]
decF3[12] <- decF3[11]

############################################################################################
#Plot Deceleration Rate
plot(t, decL3,  type = "b", ylim = c(-10, 10), pch=5, col = "red", main = "Deceleration Rate", xlab = "Time (s)", ylab = "Deceleration Rate")
par(new = TRUE)
lines(t, decF3,  pch=18, type = "b", col = "blue",lty=2) 
legend(1, 9.5, legend=c("Leading", "Following"),
       col=c("red", "blue"), lty=1:2, cex=1)

# ***********************************************************************************************************
# 1) Difference of Space distance and Stopping distance- DSS [REF 45 do MAHMUD]
# ***********************************************************************************************************
#DSS <- function(Vf, Vl, dT, u, dist, g) {
# VF = Following Vehicle Speed
# VL = Leader Vehicle Speed
# dT = Reaction time (Mean Reaction time = 1.5s)
# u = Friction Coefficient (DRY = 0.7 and WET = =.4)
# dist = distance between Leading vehicle and Following vehicle [m]
# g = Gravity Acceleraiton (9.8)

DSSvector3 <- numeric(12)
for(i in 1:12){
  DSSvector3[i] <- DSS(VF3[i], VL3[i], 1.5, 0.7, Ddist3[i], 9.8)
}
plot(t, DSSvector3,  type = "b", pch=5, col = "orange",  main = "DSS  x T[s]", xlab = "Time (s)", ylab = "DSS [m]")

# ***********************************************************************************************************
# 2) TTC calculus for this Scenario
# A sigla TTC faz alusão à Time To Collision - TTC; irá calcular o tempo para colisão
# ***********************************************************************************************************
#TTC <- function(dist, Lv, Vf, Vl) 
# dist = Distance between vehicles,       
# Lv = length of leading vehicle
# Vf = Following vehicle, 
# Vl = Leading vehicle

TTCvector3 <- numeric(12)
for(i in 1:12) {
  TTCvector3[i] <- TTC(Ddist3[i],5,VelF3.df$y[i], VelL3.df$y[i])
}
# Plot TTC index 
plot(t, TTCvector3,  type = "b", pch=5, col = "orange",  main = "TTC index  x T[s]", xlab = "Time (s)", ylab = "TTC index")

# ***********************************************************************************************************
# 3) Time to collision with disturbance - TTCD calculus for this Scenario
# ***********************************************************************************************************
#TTCD <- function(V1, V2, L0, Lv, d){
#Vl = v1 = Speed of the leading vehicle [m/s]
#Vf = v2 = Speed of the following vehicle (constant in the car following scenario)
#L0 = Initial relative distance between the leading and the following vehicle
#Lv = length of leading vehicle
# d = The deceleration rate of the leading vehicle
TTCDvector3 <- numeric(12)
iTTCDvector3 <- numeric(12)
for (i in 1:12) {
  TTCDvector3[i] <- TTCD(tF3[i], VL3[i], VF3[i], Ddist3[1], 5, decL3[i])
  iTTCDvector3[i] <- iTTCD(TTCDvector3[i])
}
#TTCD.df <- data.frame(tF3, VL3, VF3, Ddist3, 5, decF3, TTCDvector3,iTTCDvector3)
#View(TTCD.df)
#View(TTCDvector3)
# Plot TTCDvector3 index 
plot(t, TTCDvector3,  type = "b", pch=5, col = "orange",  main = "TTCD index  x T[s]", xlab = "Time (s)", ylab = "TTCD index")

plot(t, iTTCDvector3,  type = "b", pch=5, col = "pink",  main = "iTTCD index  x T[s]", xlab = "Time (s)", ylab = "iTTCD index")

# ***********************************************************************************************************
# 4) Criticality Index Function - CIF (CIF = V^2/TTC)
# ***********************************************************************************************************
# CIF <- function(V, TTCi)
CIFvector3 <- numeric(12)
for(i in 1:12){
  CIFvector3[i] <- CIF(VelF3.df$y[i], TTCvector3[i])
}
plot(t, CIFvector3,  type = "p", pch=5, col = "blue",  main = "CIF index", xlab = "Time (s)", ylab = "CIF index")
# ***********************************************************************************************************
# 5) MTTC calculus for this Scenario
# ***********************************************************************************************************
# MTTC <- function(deltaV, deltaA, D)
# deltaV = Relative Speed
# deltaA = Relative Acceleration
#      D = Initial Relative Space Gap

MTTCvector3 <- numeric(12)
iMTTCvector3 <- numeric(12)
lambda3 <- numeric(12)
Fator3 <- numeric(12)
CPivector3 <- numeric(12)
CPiNormaL3 <- numeric(12)
t <- seq(12)
for(i in 1:12){
  MTTCvector3[i] <- MTTC(DeltaV3[i], DeltaA3[i], Ddist3[i])
  iMTTCvector3[i] <- iMTTC(MTTCvector3[i])

############### CÁLCULO DO CPi A PARTIR DO MTTC: TESE DO (YANG, 2012) #########
  lambda3[i] <- 1.4419*MTTCvector3[i] - 0.0012
  Fator3[i] <- ((-1)*MTTCvector3[i])/lambda3[i]
  CPivector3[i] <- 100*exp(Fator3[i])
}
CPiMAX <- max(CPivector3)

for(j in 1:12){
  CPiNormaL3[i] <- CPivector3[i]/CPiMAX
}
MTTC.df <- data.frame(DeltaV3, DeltaA3, Ddist3, lambda3, Fator3, MTTCvector3, iMTTCvector3, CPivector3)

par(mfrow=c(2, 1))
plot(t, MTTCvector3,  type = "o", pch=5, col = "blue",  main = "MTTC index", xlab = "Time (s)", ylab = "MTTC index")

plot(t, iMTTCvector3,  type = "o", pch=5, col = "pink",  main = "iMTTC index", xlab = "Time (s)", ylab = "iMTTC index")

plot(t, CPiNormaL3,  ylim = c(0,1), type = "o", pch=5, col = "pink",  main = "CPi index", xlab = "Time (s)", ylab = "CPi index")

# ***********************************************************************************************************
# 6) Crash Index calculus for this Scenario
# ***********************************************************************************************************
# CI <- function(vf, af, MTTCi, vl, al){
# vf    = Folowing Vehicle Speed [m/s]
# vl    = Leading Vehicle Speed
# af    = Following Vehicle Acceleraiton
# al    = Leading Vehicle Acceleraiton  
# MTTCi = Modified Time to Collision index

CIvector3 <- numeric(12) 
iCIvector3 <- numeric(12) 
for(i in 1:12) {
  CIvector3[i] <- CI(VF3[i], AccelF3.df$y[i], MTTCvector3[i], VL3[i], AccelL3.df$y[i])
  iCIvector3[i] <- iCI(CIvector3[i])
}
#Plot Deceleration Rate
plot(t, CIvector3,  type = "b", pch=5, col = "blue",  main = "Crash Index", xlab = "Time (s)", ylab = "Crash Index")

plot(t, iCIvector3,  type = "b", pch=5, col = "pink",  main = "iCrash Index", xlab = "Time (s)", ylab = "iCrash Index")

# ***********************************************************************************************************
# 7) DRAC vector calculus for this Scenario
# ***********************************************************************************************************
DRACvector3 <- numeric(12)
for(i in 1:12) {
  
# Deceleration Rate to Avoid Crash (DRAC)
#DRAC <- function(Vf, Vl, dist, Lv)    # v1 = Initial speed of the leading vehicle
#{                                     # v2 = Initial speed of the following vehicle (constant in the car following scenario)
                                      # dist = Distance between vehicles,
                                      # Lv = length of leading vehicle
  
  DRACvector3[i] <- DRAC(VF3[i], VL3[i], abs(Ddist3[i]), 5)
}
#Plot DRAC index
plot(t, DRACvector3,  type = "c", pch=5, col = "purple",  main = "DRAC index  x T[s]", xlab = "Time (s)", ylab = "DRAC index")

###############################################################################
#iDRAC
iDRACvector3 <- numeric(12)
for (i in 1:12) {
   iDRACvector3[i] <- iDRAC(DRACvector3[i])
}
#Plot iDRAC index
plot(t, iDRACvector3,  type = "c", pch=5, col = "purple",  main = "iDRAC index  x T[s]", xlab = "Time (s)", ylab = "iDRAC index")

########## Vá para a LINHA 765 e clique no Triângulo EXECUTAR #################

```


# AHP FUNCTION MODEL USE
```{r}
#AHP <- function(PS11, PS12, PS13, PS14, PS15,
#                PS21, PS22, PS23, PS24, PS25,
#                PS31, PS32, PS33, PS34, PS35,
#                PS41, PS42, PS43, PS44, PS45,
#                PS51, PS52, PS53, PS54, PS55,
#                C11,  C16,  C21,  C26,  C31){
# c11 = iTTCD  input value
# c16 = iDRAC  input value
# c21 = iMTTC  input value
# c26 = iCI    input value
# c31 = IDdist input value
hazard3 <- numeric(12)
decision3 <- numeric(12)
t <- seq(12)
for(i in 1:12)
{
  hazard3[i]   <- AHP(  1,   5,   1/5,    4,  1/2,
                      1/5,   1,   1/3,  1/9,    1,
                        5,   3,     1,    2,    1,
                      1/4,   9,   1/2,    1,    3,
                        2,   1,     1,  1/3,    1,
 iTTCDvector3[i],iDRACvector3[i], iMTTCvector3[i], iCIvector3[i], iDdist3[i])[2]

  decision3[i] <- AHP(  1,   5,   1/5,    4,  1/2,
                      1/5,   1,   1/3,  1/9,    1,
                        5,   3,     1,    2,    1,
                      1/4,   9,   1/2,    1,    3,
                        2,   1,     1,  1/3,    1,
iTTCDvector3[i],iDRACvector3[i], iMTTCvector3[i], iCIvector3[i], iDdist3[i])[1]
 
}
plot(t, hazard3,  type = "b", ylim = c(0,100), pch=5, col = "brown",  main = "hazard percent", xlab = "Time (s)", ylab = "hazard percent")

plot(t, DeltaSLcumullate3.df$y,  ylim = c(0, 1600), type = "b", pch=5, col = "red",  main = "Cumulative spatial displacement", xlab = "Time (s)", ylab = "Cumulative spatial displacement [m]")
par(new = TRUE)
lines(t, DeltaSFcumullate3.df$y, pch=18, type = "b", col = "blue",lty=2) 
#legend(1, 1800, legend=c("Leader", "Following"), col=c("red", "blue"), lty=1:2, cex=1)

####################### Go to LINE 805 and CLICK To Execute ##################
```

#SOBEPOSIÇÃO DE INDICES
```{r}
#library(plotly)
#require(plotly)
t <- seq(12)
indices3.df <- data.frame(t, round(TTCDvector3, 2), round(iDRACvector3, 2), round(MTTCvector3, 2), round(CIvector3, 2), round(DRACvector3, 2))
indexes3.df <- data.frame(iTTCDvector3,iDRACvector3, iMTTCvector3,iCIvector3)
#View(indexes.df)
fig <- ggplot(data=indexes3.df, aes(x=t)) + labs(title = "Sobreposição dos diferentes indexes") + xlab("Tempo [s]") + 
  ylab("Índice") + xlim(1, 12) + ylim(0, 100) +
  geom_line(aes(y = iTTCDvector3), color = "darkred", linetype=1, size = 3) + 
  geom_line(aes(y = iDRACvector3), color="darkgreen", linetype=1, size = 2) +  
  geom_line(aes(y = iMTTCvector3), color = "blue",    linetype=2, size = 2) +   
  geom_line(aes(y = iCIvector3),   color="steelblue", linetype=6, size = 2) +
  scale_color_manual(name="TITLE")+
  guides(colour = guide_legend(override.aes = list(linetype = 1)))
ggplotly(fig)
############### Vá para a LINHA 825 e clique no Triângulo EXECUTAR ############
```

#SOBEPOSIÇÃO DE INDICES + HAZARD PERCENTAGE 
```{r}
i3.df <- merge(indices3.df,indexes3.df)
for(l in 1:12){
  decisao <- merge(hazard3[l],decision3[l])
}
for(l in 1:12){
  decisao[l,] <- merge(hazard3[l],decision3[l])
}
ph <- sprintf("%.2f", c(hazard3[1], hazard3[2], hazard3[3], hazard3[4], hazard3[5], hazard3[6], hazard3[7], hazard3[8], hazard3[9], hazard3[10], hazard3[11], hazard3[12]))
resumo3.df <- data.frame(as.numeric(t), 
                        as.numeric(sprintf("%.2f", DeltaSLcumullate3.df$y)),
                        as.numeric(sprintf("%.2f", DeltaSFcumullate3.df$y)),
                        as.numeric(sprintf("%.2f", iTTCDvector3)),
                        as.numeric(sprintf("%.2f", iDRACvector3)),
                        as.numeric(sprintf("%.2f", iMTTCvector3)),
                        as.numeric(sprintf("%.2f", iCIvector3)),
                        as.numeric(sprintf("%.2f", iDdist3)),
                        as.numeric(ph),
                        decisao[,2])
names(resumo3.df) <- c("TIME", "DeltaSLcumullate", "DeltaSFcumullate", "TTCD", "DRAC", "MTTC", "CI", "iDdist", "HAZARD", "DECISION")
View(resumo3.df)
write.csv2(resumo3.df, "C:\\WYOMING2\\DataFrames\\resultadosCENARIO3_R05.csv")

#library(plotly)
#require(plotly)
t <- seq(12)
fig <- ggplot(data=Vel.df, aes(x=t)) + labs(title = "GRAPHIC OVERLAY") + xlab("TIME [s]") + 
  ylab("INDEXES VALUES") + xlim(1, 12) + ylim(0, 1600) +
  geom_line(aes(y = DeltaSLcumullate3.df$y), color = "red",  linetype=5, size = 2) + 
  geom_line(aes(y = DeltaSFcumullate3.df$y), color = "blue",     linetype=6, size = 2) +  
  geom_line(aes(y = resumo3.df$TTCD),        color = "darkred",  linetype=1, size = 1) + 
  geom_line(aes(y = resumo3.df$DRAC),        color = "green",    linetype=2, size = 1) +   
  geom_line(aes(y = resumo3.df$MTTC),        color = "steelblue",linetype=3, size = 1) +
  geom_line(aes(y = resumo3.df$CI),          color = "darkgreen",linetype=4, size = 1) +
  geom_line(aes(y = resumo3.df$HAZARD),      color = "red",      linetype=5, size = 2) +
  geom_line(aes(y = resumo3.df$iDdist),      color = "orange",   linetype=7, size = 2) +  
  scale_color_manual(name="VEHICLES VELOCITY")+
  guides(colour = guide_legend(override.aes = list(linetype = 1)))
ggplotly(fig)

####################### Go to LINE 870 and CLICK To Execute ###################

```


```{r}
par(mfrow=c(3, 2))

### 01)Plot Cumulative spatial displacement 
plot(t, DeltaSLcumullate3.df$y,  ylim = c(-200, 2000), type = "b", pch=5, col = "red",  main = "Cumulative spatial displacement", xlab = "Time (s)", ylab = "Cumulative spatial displacement [m]")
par(new = TRUE)
lines(t, DeltaSFcumullate3.df$y, pch=18, type = "b", col = "blue",lty=2) 
#legend(1, 1800, legend=c("Leader", "Following"), col=c("red", "blue"), lty=1:2, cex=1)

### 02)Plot TTC index 
plot(t, TTCvector3,  type = "b", pch=5, col = "black",  main = "TTC x Time", xlab = "Time [second]", ylab = "TTC index")

### 03)TTCD
plot(t, TTCDvector3,  type = "b", pch=5, col = "black",  main = "TTCD x Time", xlab = "Time [second]", ylab = "TTCD index")

### 04)MTTC index
plot(t, MTTCvector3,  type = "o", pch=5, col = "black",  main = "MTTC x Time", xlab = "Time [second]", ylab = "MTTC index")

### 05)Plot DRAC index
plot(t, DRACvector3,  type = "c", pch=5, col = "purple",  main = "DRAC x Time", xlab = "Time [second]", ylab = "DRAC index")

### 06) CRASH INDEX
plot(t, CIvector3,  type = "b", pch=5, col = "black",  main = "Crash Index x Time", xlab = "Time [second]", ylab = "Crash Index")

####################### Go to LINE 900 and CLICK To Execute ###################

```



```{r}
par(mfrow=c(3, 2))

### 01)Plot Cumulative spatial displacement 
plot(t, DeltaSLcumullate3.df$y,  ylim = c(-200, 2000), type = "b", pch=5, col = "red",  main = "Cumulative spatial displacement", xlab = "Time (s)", ylab = "Cumulative spatial displacement [m]")
par(new = TRUE)
lines(t, DeltaSFcumullate3.df$y, ylim = c(0, 1000), pch=18, type = "b", col = "blue",lty=2) 
#legend(2, 800, legend=c("Leader", "Following"), col=c("red", "blue"), lty=1:2, cex=1)

### 02)Plot TTC index 
plot(t, TTCvector3,  type = "b", pch=5, col = "black",  main = "TTC x Time", xlab = "Time [second]", ylab = "TTC index")

### 03)TTCD
plot(t, iTTCDvector3,  type = "b", pch=5, col = "red",  main = "iTTCD x Time", xlab = "Time [second]", ylab = "TTCD index")

### 04)MTTC index
plot(t, iMTTCvector3,  type = "o", pch=5, col = "red",  main = "iMTTC x Time", xlab = "Time [second]", ylab = "MTTC index")

### 05)Plot DRAC index
plot(t, iDRACvector3,  type = "c", pch=5, col = "red",  main = "iDRAC x Time", xlab = "Time [second]", ylab = "DRAC index")

### 06) CRASH INDEX
plot(t, iCIvector3,  type = "b", pch=5, col = "red",  main = "iCrash Index x Time", xlab = "Time [second]", ylab = "Crash Index")

###############################################################################
par(mfrow=c(3, 2))

### 07)Plot Cumulative spatial displacement 
plot(t, DeltaSLcumullate3.df$y,  ylim = c(-200, 2000), type = "b", pch=5, col = "red",  main = "Cumulative spatial displacement", xlab = "Time (s)", ylab = "Cumulative spatial displacement [m]")
par(new = TRUE)
lines(t, DeltaSFcumullate3.df$y, ylim = c(0, 1000), pch=18, type = "b", col = "blue",lty=2) 
#legend(2, 800, legend=c("Leader", "Following"), col=c("red", "blue"), lty=1:2, cex=1)

### 08) ACELERATION  data
plot(t, AccelL3.df$y, ylim = c(-40,10), type = "b", pch=5, col = "red",  main = "Vehicles Accelerations", xlab = "Time (s)", ylab = "Acceleration[m/s-2])")
par(new = TRUE)
lines(t, AccelF3.df$y,  type = "b", pch=18, col = "blue",  main = "Following Vehicle Acceleration", xlab = "Time (s)", ylab = "Acceleration[m/s-2])")
legend(1, -5, legend=c("Leading", "Following"),
       col=c("red", "blue"), lty=1:2, cex=1)

### 09) Distance Between Vehicles x iDdist Index
plot(t, Ddist3, ylim = c(-1500, 5000), type = "b", pch=5, col = "black",  main = "Distance between vehicles[m]  x T[s]", xlab = "Time (s)", ylab = "Distance between vehicles[m]")
par(new = TRUE)
lines(t, iDdist3, pch=18, type = "b", col = "orange",lty=2)
legend(9.2, 4800, legend=c("Ddist", "iDdist"), col=c("black", "orange"), lty=1:2, cex=1)

### 10) Plot Deceleration Rate
plot(t, decL3,  type = "b", ylim = c(-25, 20), pch=5, col = "red", main = "Deceleration Rate", xlab = "Time (s)", ylab = "Deceleration Rate")
par(new = TRUE)
lines(t, decF3,  pch=18, type = "b", col = "blue",lty=2) 
legend(8, -2, legend=c("Leading", "Following"),
       col=c("red", "blue"), lty=1:2, cex=1)

### 11) HAZARD PORCENTAGE
plot(t, hazard3,  type = "b", ylim = c(0,100), pch=5, col = "brown",  main = "HAZARD PORCENTAGE", xlab = "Time (s)", ylab = "hazard percent")

### 12) Criticality Index Function - CIF (CIF = V^2/TTC)
plot(t, CIFvector3,  type = "p", pch=5, col = "black",  main = "CIF x Time", xlab = "Time [second]", ylab = "CIF index")
```

